\Large Postdoctoral Position in Exoplanet Theory Research Proposal: \\ The Role of Disk Volatile Chemistry and Dynamics in Shaping the Compositions of Nascent Planets\vspace{-2ex}

### 2015-11-13 Postdoc Applications/AnaMariaPisoResearchProposal.tex
update

The results from parts 1 and 2 will feed into a \textbf{large planet synthesis model}, in which I will use a grid of different \textbf{initial disk and planetary embryo conditions}. I will develop my own numerical program instead of using already existing codes of planet population synthesis (e.g., $[10]$ and references therein), since the latter involve many complex physical processes, some of which might not be necessary or relevant for my own calculations. In contrast, for this computationally expensive step, I will only include the processes that I have identified to be the most important in the local simulations from steps 1 and 2. This will allow me to \textbf{constrain a planet's formation location based on its chemical composition}. Comparing my results with current observations of atmospheric spectra (e.g., Figure 3 from $[4]$), and more importantly future JWST observations, will lead to great scientific strides in understanding the complex connection between protoplanetary disks and the formation, evolution and composition of exoplanets.

@@

\textbf{The University of Chicago is the ideal place for me to pursue my postdoctoral research}, due to its vibrant community of experts in protoplanetary disks and exoplanets, both in the Department of Astronomy and Department of Geophysical Sciences. I would love the opportunity to work with \textbf{Prof. Leslie Rogers}, an expert in planetary interiors and atmospheres --- such a collaboration would be instrumental in achieving my research goals during my postdoctoral tenure and afterwards. In the Department of Geophysical Sciences, I would like to collaborate with \textbf{Prof. Fred Ciesla}, a leader in protplanetary disk dynamics, chemical composition and evolution. Additionally, the Department of Astronomy hosts experts in detecting and characterizing worlds outside the Solar system, such as \textbf{Prof. Dan Fabrycky} and \textbf{Prof. Jacob Bean}, which presents great prospects in connecting my theoretical research work with observations.

@@

\section*{References}
\footnotesize
%\begin{thebibliography} {9}
\noindent $[1]$ Batalha, N. M. 2014, Proceedings of the National Academy of Science, 111, 12647 \\
$[2]$ Lissauer J. J., Dawson R. I., Tremaine S., 2014, Nature, 513, 336 \\
$[3]$ Debes, J. H., Jang-Condell, H., Weinberger, A. J., Roberge, A., \& Schneider, G. 2013, ApJ, 771, 45 \\
$[4]$ Kreidberg, L., Line, M. R., Bean, J. L., et al. 2015, ArXiv e-prints, arXiv:1504.05586 \\
$[5]$ Piso, A.-M. A., \& Youdin, A. N. 2014, ApJ, 786, 21 \\
$[6]$ Piso, A.-M. A., Youdin, A. N., \& Murray-Clay, R. A. 2015, ApJ, 800, 82 \\
$[7]$ Piso, A.-M. A., Öberg, K.I., Birnstiel, T, \& Murray-Clay, R.M., ApJ, resubmitted after referee report \\
$[8]$ ALMA Partnership et al., 2015, ApJ, 808, L3 \\
$[9]$ \"Oberg, K. I., Murray-Clay, R., \& Bergin, E. A. 2011, ApJ, 743, L16 \\
$[10]$ Ida, S., Lin, D. N. C., \& Nagasawa, M. 2013, ApJ, 775, 42 \\
$[11]$ Semenov, D., \& Wiebe, D. 2011, ApJS, 196, 25
%\end{thebibliography}

>>>>

The results from parts 1 and 2 will feed into a \textbf{large planet synthesis model}, in which I will use a grid of different \textbf{initial disk and planetary embryo conditions}. I will develop my own numerical program instead of using already existing codes of planet population synthesis (e.g., $[10]$ and references therein), since the latter involve many complex physical processes, some of which might not be necessary or relevant for my own calculations. To minimize computational expenses, I will build a program from bottom-up that includes select physical and chemical processes based on the local simulations from steps 1 and 2. This will allow me to predict the \textbf{range of planet compositions that can form under reasonable disk conditions}, as well as \textbf{constrain a planet's formation location based on its chemical composition}. Comparing my results with current observations of atmospheric spectra (e.g., Figure 3 from $[4]$), and more importantly future JWST observations, will lead to great scientific strides in understanding the complex connection between protoplanetary disks and the formation, evolution and composition of exoplanets.

@@

\textbf{The University of Chicago is the ideal place for me to pursue my postdoctoral research}, due to its vibrant community of experts in protoplanetary disks and exoplanets, both in the Department of Astronomy and Department of Geophysical Sciences. I would love the opportunity to work with \textbf{Prof. Leslie Rogers}, an expert in planetary interiors and atmospheres --- such a collaboration would be instrumental in achieving my research goals during my postdoctoral tenure and afterwards. In the Department of Geophysical Sciences, I would like to collaborate with \textbf{Prof. Fred Ciesla}, a leader in protplanetary disk dynamics, chemical composition and evolution. Additionally, the Department of Astronomy hosts experts in detecting and characterizing worlds outside the Solar system, such as \textbf{Prof. Dan Fabrycky} and \textbf{Prof. Jacob Bean}, which presents great prospects in connecting my theoretical research work with observations. \\

@@

%\section*{References}
\footnotesize
%\begin{thebibliography} {9}
\noindent $[1]$ Batalha, N. M. 2014, Proceedings of the National Academy of Science, 111, 12647 \\
$[2]$ Lissauer J. J., Dawson R. I., Tremaine S., 2014, Nature, 513, 336 \\
$[3]$ Debes, J. H., Jang-Condell, H., Weinberger, A. J., Roberge, A., \& Schneider, G. 2013, ApJ, 771, 45 \\
$[4]$ Kreidberg, L., Line, M. R., Bean, J. L., et al. 2015, ArXiv e-prints, arXiv:1504.05586 \\
$[5]$ Piso, A.-M. A., \& Youdin, A. N. 2014, ApJ, 786, 21 \\
$[6]$ Piso, A.-M. A., Youdin, A. N., \& Murray-Clay, R. A. 2015, ApJ, 800, 82 \\
$[7]$ Piso, A.-M. A., Öberg, K.I., Birnstiel, T, \& Murray-Clay, R.M., ApJ, resubmitted after referee report \\
$[8]$ ALMA Partnership et al., 2015, ApJ, 808, L3 \\
$[9]$ \"Oberg, K. I., Murray-Clay, R., \& Bergin, E. A. 2011, ApJ, 743, L16 \\
$[10]$ Ida, S., Lin, D. N. C., \& Nagasawa, M. 2013, ApJ, 775, 42 \\
$[11]$ Semenov, D., \& Wiebe, D. 2011, ApJS, 196, 25
%\end{thebibliography}
